Introducing the \NAME Framework\\ for Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-16 paper.tex
added design FCF & Code Model

\subsection{Function Code Fusion}

>>>>

\subsection{Functional Code Fusion}

Thanks to the functional description of events and the effects that are
triggered by them, the code generator is able to identify the same actions
across different algorithms. This way it is possible to extract the parsing of
incoming messages, group actions on the same sets of data or scheduled function
executions.

FCF typically looks for patterns in the semantic model and performs model
transformations to change these patterns to a more optimized organization.
Semantic transformations are performed on the semantic model itself and end
with a transformation of the semantic model into a code model, which encodes
the semantics into technical code constructs.

\subsection{Code Model}

The code model can be compared to an AST for a very expressive language. It
contains constructs found in certain languages, but not in others. Therefore a
second round of model transformations needs to be performed. These syntactic
transformations morph the unsupported constructs into comparable constructs
that are supported by the targeted platform and language.

Depending on the target platform, some of the constructions used to e.g. parse
incoming messages, schedule tasks,\dots may not be transformed into
self-containing code. The generator then uses a software library to perform
these tasks. It will look for patterns that indicate any of these actions and
transform them into calls into the \NAME software library.
